Bayesian determination of the effect of a deep euctectic solvent on the structure of lipid monolayers

### 2018-09-05 reports/paper.tex
after most of karens comments

It has recently been shown that these solvents have the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect. The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to potential application in the preservation of biomolecules as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES have been able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}

@@

The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This is a method for sampling a high-dimensionality parameter space, such as that which is relevant in reflectometry fitting, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously. The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found as well as information about the correlations between different variables.

@@

The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum. Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}

DPPC (> 99 \%, C$_{16}$ tails), DMPC (> 99 \%, C$_{14}$ tails), and DMPG (> 99 \%, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (> 99 \%, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received. Deuterated versions of DPPC (d$_{62}$-DPPC, > 99 \%, deuterated tails-only) and DMPC (d$_{54}$-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification. These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature. PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphoditylglycerol head component, these are shown in Figure \ref{fig:heads}.

@@

\begin{table*}
	\small
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
	\label{tab:water}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llllllllll}
		\hline
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
    \hline
    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
	\end{tabular*}
\end{table*}
In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration. After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface. Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough. In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough. Instead, small Delrin adsorption troughs were used that did not have controlable barriers. So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.

@@

\subsection{Data analysis}
The use of XRR and NR to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} The models used in the rationalisation of XRR and NR data have varied significantly in number of layers present, use of interfacial roughness, and parameterisation of physical constraints. Frequently these physical constraints include the component volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}. Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} suggests possible oversights in the modelling of NR data.

In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) head is in the range from 320-360 \AA$^3$ while the phosphatidylglycerol (PG) head is in the range 289-291 \AA$^3$. However, we do not know whether the head component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent. The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}

@@

In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations. The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, an assumption that is based on our belief that increasing surface pressure should not significantly influence the head layer thickness. The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given. The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied. For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process. Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.

%
\begin{table}[h]
	\small
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
		\hline
	\end{tabular*}
\end{table}
%
In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements. This approach means that the number of variable parameters to fir the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets. Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data. The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the PDF associated with each parameter. In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations. The use of MCMC sampling allowed for the Bayesian inference of the probability density function for each of the variables and their respective interactions (shown in detail in the ESI). This allowed asymmetric confidence intervals to be found for each of the variable parameters. However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e. they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up. The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
%
\section{Results \& Discussion}
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid. The resulting XRR profiles, associated SLD profiles are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varying parameters for each lipid at the highest surface pressure measured, as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively, each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.

The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure. The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}. Table \ref{tab:neutron} gives details of the varying parameters at each surface pressure as well as the details of the $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively; again these are given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
%
\begin{table}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured. The values of $d_t$ were found from the appropriate values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the appropriate use of Eqn. \ref{equ:phih}}
	\label{tab:liptab}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
		\hline
	\end{tabular*}
\end{table}
%

@@

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_other_data}
	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipresults}
\end{figure}
%
The variation of the tail layer thickness in the models, found from $\theta_t$ using Eqn \ref{equ:tl}, with surface pressure is given for each lipid in Figure \ref{fig:lipresults}. It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateuing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC the plateu can be assumed to be at higher pressures than those studied. This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.

\subsection{Effect of compression on solvent concentration}
In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer. This can be rationalised by considering when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk. A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface.\cite{Bayerl1990}

\subsection{Effect of compression on the lipid tail component volumes}
It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques. It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails. However, this reduction observed has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure. In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.

>>>>

It has recently been shown that these solvents have the ability to promote the self-assembly of surfactants into micellar structures\cite{Sanchez-Fernandez2016,Arnold2015} and to stabilise the conformation of non-ionic polymer species,\cite{Sapir2016} indicating the presense of a solvophobic effect. The behaviour and conformation of biomolecules in DES have seen an increase in interest,\cite{Esquembre2013,Gorke2010,Gorke2008,Monhami2014,Wu2014,Harifi-Mood2017,Milano2017,Sanchez-Fernandez2017} due to the potential application of DES as environments for enzymatic reactions.\cite{Merza2018} Futhermore, recent investigations have also shown that DES are able to support the formation of phospholipid bilayers.\cite{Bryant2017,Bryant2016,Gutierrez2009}

@@

The use of a Python library for fitting enables powerful probability distribution function (PDF) sampling methods to be used such as the Goodman \& Weare Affine Invariant Markov chain Monte Carlo (MCMC) Ensemble,\cite{Goodman2010} as implemented in the Python library emcee.\cite{Foreman-Mackey2013} This is a method for sampling a high-dimensionality parameter space, such as that which is relevant in reflectometry fitting, in a Bayesian fashion, where the new samples are generated with consideration of those sampled previously. The use of Bayesian inference allows the PDF for each fitting variable to be probed, therefore estimations of the inverse uncertainties associated with each parameter can be found, as well as information about the correlations between different variables.

@@

The water content of the DES was determined before and after each experiment by Karl-Fischer titration (Mettler Toledo DL32 Karl-Fischer Coulometer, Aqualine Electrolyte A, Aqualine Catholyte CG A) in order to ensure water presence was kept to a minimum. Those measurements showed that the water content of the solvent was kept below 0.3 wt\% during all the experimental procedures presented here, which we assume to be negligible and have to little impact on the characteristics of the DES.\cite{Hammond2016,Hammond2017}

DPPC (> 99 \%, C$_{16}$ tails), DMPC (> 99 \%, C$_{14}$ tails), and DMPG (> 99 \%, C$_{14}$ tails) were supplied by Avanti Polar Lipids and DLPC (> 99 \%, C$_{12}$ tails) was supplied by Sigma-Aldrich and all were used as received. Deuterated versions of DPPC (d$_{62}$-DPPC, > 99 \%, deuterated tails-only) and DMPC (d$_{54}$-DPPC, > 99 \%, deuterated tails-only) were supplied by Avanti Polar Lipids and used without further purification. These phospholipids were dissolved in chloroform (0.5 mg/mL) at room temperature. PC indicates the molcule contains a phosphocholine head component, where PG contains a phosphatidylglycerol head component, these are shown in Figure \ref{fig:heads}.

@@

\begin{table*}
	\small
	\caption{\ Lipid component volumes extracted from different literature sources. $V_l$ corresponds to the total lipid volume, MD to molecular dynamics simulation, WAXS to wide-angle X-ray scattering, NB to neutral buoyancy and DVTD to differential vibrating tube densimetry. $^a$ The values for the head component in Kucerka \emph{et al.},\cite{Kucerka2004} were taken from Balgav\'{y} \emph{et al}.\cite{Balgavy2001}}
	\label{tab:water}
	\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l|lll|ll|ll|l|l}
		%\hline
    Lipid & DPPC & & & DMPC & & DLPC & & DMPG & POPG \\
    \hline
    Reference & [\citen{Armen1998}] & [\citen{Sun1994}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Armen1998}] & [\citen{Kucerka2004,Balgavy2001}]$^a$ & [\citen{Pan2012}] & [\citen{Kucerka2012}] \\
    \hline
    $V_l$/\AA$^3$ & $1287.3\pm25.5$ & $1148\pm2$ & $1264.2\pm32.1$ & $1172.5\pm25.1£$ & $1155.4\pm30.0£$ & $1057.7\pm24.7$ & $1046.6\pm28.0$ & $1011.4$ & $1203$ \\
    $V_t$/\AA$^3$ & $966.4\pm5.4$ & $829\pm4$ & $924.7\pm17.6$ & $851.5\pm5.0£$ & $815.9\pm15.5£$ & $736.8\pm4.6$ & $707.1\pm13.5$ & $720.4$ & $914$ \\
    $V_h$/\AA$^3$ & $320.9\pm20.1$ & $319\pm6$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $320.9\pm20.1$ & $339.5\pm14.5$ & $291.0$ & $289$ \\
    Method & MD & WAXS & NB & MD & NB & MD & NB & DVTD & MD \\
    T/$^\circ$C & 50 & 24 & 30 & 50 & 30 & 50 & 30 & 20 & 25 \\
    %\hline
	\end{tabular*}
\end{table*}
In the XRR experiment, sample preparation was performed in situ using the standard method for the spreading of insoluble monolayers on water: a certain amount of the phospholipid solution was spread onto the liquid surface in order to provide a given surface concentration. After the evaporation of the chloroform, it is assumed that the resulting system is a solvent subphase with a monolayer of phospholipid at the interface. Surface concentration was modified by closing and opening the PTFE barriers of a Langmuir trough. In order to minimise the volumes used in the NR experiment (to keep the cost of deuterated compounds to a manageable level) it was not possible to use a Langmuir trough. Instead, small Delrin adsorption troughs were used that did not have controllable barriers. So, although the surface coverage was nominally the same as used in the X-ray studies, the lack of precise control over the surface pressure meant that it was not appropriate to co-refine XRR and NR contrasts together.

@@

\subsection{Data analysis}
The use of XRR and NR to analyse the structure of phospholipids on the surface of water has a history extending over many years.\cite{Mohwald1990,Kewalramani2010,Bayerl1990,Johnson1991,Clifton2012,Helm1987,Daillant1990} The models used in the rationalisation of XRR and NR data have varied significantly in number of layers present, use of interfacial roughness, and parameterisation of physical constraints. Frequently these physical constraints include the component volumes of the phospholipid head and tail components, using values taken from other techniques, such as those shown in Table \ref{tab:water}. Additionally, a recent evaluation of the applicability of different models to surfactant and phospholipid monolayers from the NR perspective has been published,\cite{Campbell2018} that suggests possible oversights in the modelling of NR data.

In Table \ref{tab:water}, there appears to be a general consensus that the component volume of the phosphocholine (PC) head is in the range from 320-360 \AA$^3$ while the phosphatidylglycerol (PG) head is in the range 289-291 \AA$^3$. However, we do not know whether the head component volumes used in the literature, that are derived from water-based measurements, will be appropriate for this work, which involves a non-aqueous solvent. The charged nature of the zwitterionic and anionic lipid heads means that they are likely to have different interactions with polar, but neutral, water as compared to the charged DES components.\cite{Sanchez-Fernandez2018} Furthermore, it has been shown that in the liquid expanded and condensed phases, which are often present at high surface pressure, the lipid tails will become compressed resulting in a component volume less than measured from other techniques,\cite{Marsh2010,Small1984} and the need to take into account the compaction of the hydrocarbon chains of phospholipid monolayers according to their phase in the modelling of NR data has recently been demonstrated.\cite{Campbell2018}

@@

In the first of two steps, this custom model was used to co-refine the component volume of the lipid head component, $V_h$, the volume of the tail component, $V_t$, and the head thickness, $d_h$ across XRR measurements at four different surface concentrations. The head thickness was not permitted to vary with surface pressure to reduce the dimensionality of the parameter space, an assumption that is based on our belief that increasing surface pressure should not significantly influence the head layer thickness. The following parameters were allowed to vary; $\theta_t$, and $\sigma_{t,h,s}$, independently across the surface pressures, while others, shown in Table \ref{tab:invariant}, were held constant at the values given. The length of the carbon chain was kept constant at the value determined by the Tanford equation,\cite{Tanford1980} since this is the maximum chain length possible and the most likely conformation at the surface pressures studied.\cite{Hollinshead2009} For each co-refinement of four XRR measurements, there were, in total, eleven degrees of freedom in the fitting process. Throughout all of the analysis, the reflectometry scale factor was allowed to vary freely, while the background as constrained to the intensity of either the largest or second-largest $q$-value.

%
\begin{table}[h]
	\small
	\caption{\ The invariant parameters within the chemically-consistent model.
	$^a$Values obtained from the Tanford formula.\cite{Tanford1980} $^b$Values obtained from Sanchez-Fernandez \emph{et al.}\cite{Sanchez-Fernandez2016}}
	\label{tab:invariant}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Component & $b_t$/fm & $b_h$/fm & $t_t$/\AA & $\text{SLD}$/$\times10^{-6}$\AA$^{-2}$ \\
		\hline
		X-ray & & & & \\
		DLPC & 5073 & 4674 & 15.5$^a$ & -- \\
		DMPC & 5985 & 4674 & 18.0$^a$ & -- \\
		DPPC & 6897 & 4674 & 20.5$^a$ & -- \\
		DMPG & 5985 & 4731 & 18.0$^a$ & --\\
		Air & -- & -- & -- & 0\\
		DES & -- & -- & -- & 10.8$^b$ \\
		\hline
		Neutron & & & & \\
		d$_{54}$-DMPC & 5329.8 & 602.7 & 18.0$^a$ & -- \\
		d$_{62}$-DPPC & 6129.2 & 602.7 & 20.5$^a$ & -- \\
		h-DES & -- & -- & -- & 0.43$^b$  \\
		hd-DES & -- & -- & -- & 3.15$^b$ \\
		\hline
	\end{tabular*}
\end{table}
%
In the second step, the head and tail component volumes, and head layer thickness determined from XRR were fixed for the refinement of the custom model against the NR measurements. This approach means that the number of variable parameters to fit the NR data can be reduced to two, namely the chain tilt angle, $\theta_t$, and the interfacial roughness, $\sigma_{t,h,s}$, for the co-refinement of two datasets. Table \ref{tab:invariant} also gives the details of the scattering lengths and SLDs used as invariant parameters for the NR fitting.

In both cases, the refinement of the custom model to the experimental data involved the transformation of the reflectometry calculated from the model and the data into $Rq^4$ such that the contribution of the Fresnel decay was removed, before using the differential evoluation method available to refnx from the scipy library,\cite{Jones2001} to find the parameters that gave the best fit to the data. The parameter space was then probed using the MCMC method available through emcee,\cite{Foreman-Mackey2013} which allowed for an estimate of the probability distribution function (PDF) associated with each parameter. In the MCMC sampling, 200 walkers were used over 1000 iterations, following an equilibration of 200 iterations. The use of MCMC sampling allowed for the Bayesian inference of the PDF for each of the variables and their respective interactions (shown in detail in the ESI). This allowed asymmetric confidence intervals to be found for each of the variable parameters. However, it is important to note that these are not \emph{true} confidence intervals, and account only for the uncertainty present in the data, i.e. they do no account of systematic uncertainty in the measurement that are underrepresented, or unrepresented, in the experimental dataset.

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_all_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_all_data}
	\caption{The XRR profiles (left) and SLD profiles (right) for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG, at the four measured surface pressures; lowest surface pressure at the bottom and increasing moving up. The different surface pressure XRR profiles have been offset in the $y$-axis by an order of magnitude and SLD profiles offset in the $y$-axis by $5\times10^{-6}$ \AA$^{-2}$, for clarity. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipids}
\end{figure}
%
\section{Results \& Discussion}
The chemically-consistent model was co-refined across the four surface pressure XRR measurements for each lipid. The resulting XRR profiles and associated SLD profiles are shown in Figure \ref{fig:lipids}. Table \ref{tab:liptab} gives details of all varied parameters for each lipid at the highest surface pressure measured, as well as the details of $d_t$ and $\phi_h$ which are determined from Eqns. \ref{equ:tl} and \ref{equ:phih} respectively. Each value is given with asymmetric uncertainies that corresponds to a 95 \% confidence interval of the PDF; the full PDF plots can be found in the ESI.

The custom model was used to co-refine the two contrasts of NR measurements for each lipid, at each surface pressure. The resulting NR profiles and associated SLD profiles, at a surface pressure of 20 mNm$^{-1}$ are given in Figure \ref{fig:neutron}. Table \ref{tab:neutron} gives details of the varied parameters at each surface pressure as well as $d_t$ and $\phi_h$, again determined from Eqns. \ref{equ:tl} and \ref{equ:phih}. These are, once again, given with a asymmetric uncertainties corresponding to a 95 \% confidence interval and the full PDF plots can be found in the ESI.
%
\begin{table}
	\small
	\caption{\ The best-fit values, and associated 95 \% confidence intervals for the varying parameters in the XRR models, at the highest surface pressure (SP) measured. The values of $d_t$ were found from the values of $\theta_t$ using Eqn. \ref{equ:tl} and the values for $\phi_h$ were obtained from the use of Eqn. \ref{equ:phih}}
	\label{tab:liptab}
	\begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}lllll}
		\hline
		Lipid & DLPC & DMPC & DPPC & DMPG \\
    SP/mNm$^{-1}$ & 35 & 40 & 30 & 30 \\
		\hline
		$\theta_t$/$^\circ$ & \input{../output/dlpc/angle35.txt} & \input{../output/dmpc/angle40.txt} & \input{../output/dppc/angle30.txt} & \input{../output/dmpg/angle30.txt} \\
		$\sigma_{t,h,s}$/\AA & \input{../output/dlpc/rough35.txt} & \input{../output/dmpc/rough40.txt} & \input{../output/dppc/rough30.txt} & \input{../output/dmpg/rough30.txt} \\
    \hline
    $V_t$/\AA$^3$ & \input{../output/dlpc/vt.txt} & \input{../output/dmpc/vt.txt} & \input{../output/dppc/vt.txt} & \input{../output/dmpg/vt.txt} \\
		$V_h$/\AA$^3$ & \input{../output/dlpc/vh.txt} & \input{../output/dmpc/vh.txt} & \input{../output/dppc/vh.txt} & \input{../output/dmpg/vh.txt} \\
		$d_h$/\AA & \input{../output/dlpc/head.txt} & \input{../output/dmpc/head.txt} & \input{../output/dppc/head.txt} & \input{../output/dmpg/head.txt} \\
    \hline
    $\phi_h$/$\times10^{-2}$ & \input{../output/dlpc/solh35.txt} & \input{../output/dmpc/solh40.txt} & \input{../output/dppc/solh30.txt} & \input{../output/dmpg/solh30.txt} \\
		$d_t$/\AA & \input{../output/dlpc/tail35.txt} & \input{../output/dmpc/tail40.txt} & \input{../output/dppc/tail30.txt} & \input{../output/dmpg/tail30.txt} \\
		\hline
	\end{tabular*}
\end{table}
%

@@

%
\begin{figure}
	\centering
	\includegraphics[width=0.48\textwidth]{figures/DLPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DPPC_other_data}
	\includegraphics[width=0.48\textwidth]{figures/DMPG_other_data}
	\caption{The PDFs of the head component volume (left) and variation of $d_t$ (blue squares) and $\phi_h$ (green circles) with surface pressure for each of the four lipids; (a) DLPC, (b) DMPC, (c) DPPC, (d) DMPG. Source: Datasets, figure files and running/plotting scripts are available under CC-BY.\cite{mccluskey_2018}}
	\label{fig:lipresults}
\end{figure}
%
The variation of the tail layer thickness in the models with surface pressure is given for each lipid in Figure \ref{fig:lipresults}. It can be observed that as the surface pressure increases, the thickness of the tail layer increases to a point, before plateauing; for DPPC this occurs at 20 mNm$^{-1}$, DMPC at 30 mNm$^{-1}$ and for DMPG and DLPC can be assumed to be at higher pressures than those studied. This phenomenon of the tail thickness increasing with increasing surface pressure has been noted before for DMPC\cite{Bayerl1990} and DPPC\cite{Campbell2018} at the air-water interface.

\subsection{Effect of compression on solvent concentration}
In Figure \ref{fig:lipresults}, it is clear that for all four lipids, as the surface pressure is increased there is a corresponding decrease in the percentage solvent present in the lipid head layer. This can be rationalised by considering that when the surface pressure is increased, the free volume available to the solvent between the lipid head components reduces forcing the solvent out of the lipid head layer and into the bulk. A similar effect has been observed when increasing the surface pressure from 11 mNm$^{-1}$ to 31 mNm$^{-1)}$ for a DMPC/DMPG monolayer at the air-water interface.\cite{Bayerl1990}

\subsection{Effect of compression on the lipid tail component volumes}
It can be seen by comparing Tables \ref{tab:water} and \ref{tab:liptab} that the volume of the lipid tails are significantly lower in the current measurements than found previously, by other techniques. It is unlikely that this is a result of the DES subphase, due to the hydrophobic nature of the lipid tails. However, this reduction has been shown previously,\cite{Campbell2018} where it was rationalised by the compaction of the monolayer at elevated surface pressure. In that work, the optimal value of the tail component volume for DPPC was found to be $772$ \AA${^3}$ at a surface pressure of $35$ mNm$^{-1}$, this agrees well with the value of \input{../output/dppc/vt.txt} \AA$^3$ found in this work at surface pressures of 15, 20, 25, and 30 mNm$^{-1}$.
